### 2022-12-02 definitions.tex
details

@@

>>>>

\alain{examiner les cas I,J un élement, cloture, tout, ...}

@@

citer

\begin{theorem}(ref)
{\sc resilience} is decidable for WSTS with strong upward compatibility and effective basis of $post^*$.
\end{theorem}

Il y a des pbs

\begin{proposition}
The hypothesis $post^*$ is undecidable for WSTS with strong upward compatibility.
\end{proposition}

\begin{proof}
$post^*$ donne l'accessibilité or les resert sont WSTS with strong compatibility. et l'accessibilité est undecidable.
\end{proof}

\begin{proposition}
{\sc $k$-resilience}, hence {\sc resilience}, is undecidable for effective WSTS with strong upward compatibility.
\end{proposition}

\begin{proof}
totot
\end{proof}
